---
title: "childes-db"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r childes-1}
install.packages("devtools")
devtools::install_github("langcog/childesr")
```

Gets all of the English transcripts:

```{r childes-2}
library(childesr)
d_eng_na <- get_transcripts(collection = "Eng-NA")
```

Get speech-act participants in the corpora:

```{r childes-3}
library(childesr)
d_participants <- get_participants()
```

Get instances of a particular word:

```{r childes-4}
library(childesr)
d_adam_prod <- get_tokens(corpus = "Brown",
                          role = "target_child",
                          target_child = "Adam",
                          token = c("dog", "ball"))
```

Get the utterances:

```{r childes-5}
library(childesr)
d_adam_utts <- get_utterances(corpus = "Brown",
                              target_child = "Adam")
```

Get all values for speaker role:
 [1] "Target_Child"    "Investigator"    "Mother"         
 [4] "Father"          "Adult"           "Child"          
 [7] "Unidentified"    "Camera_Operator" "Grandmother"    
[10] "Cousin"          "Brother"         "Playmate"       
[13] "Uncle"           "Aunt"            "Family_Friend"  
[16] "Teacher"         "Non_Human"       "Grandfather"    
[19] "Teenager"        "Toy"             "Visitor"        
[22] "Babysitter"      "Participant"     "Sister"         
[25] "Girl"            "Male"            "Sibling"        
[28] "Environment"     "Observer"        "Nurse"          
[31] "Doctor"          "Uncertain"       "Student"        
[34] "Clinician"       "Housekeeper"

```{r childes-6}
library(childesr)
d_participants <- get_participants(collection = "Eng-NA")
categories <- unique(d_participants$role)
print(categories)
```

```{r childes-6}
library(childesr)
d_participants <- get_participants(collection = "Eng-NA")
categories1 <- unique(d_participants$corpus_name)
print(categories1)
```

Get all utterances in English by speakers of a particular role:
(What roles should this be ideally?)

```{r childes-2}
library(childesr)
adult_utterances <- get_utterances(role_exclude = c("Target_Child", "Child"), language = "eng")
```

```{r childes-2}
library(childesr)
adult_utterances <- get_utterances(role_exclude = c("Target_Child", "Child"), language = "eng")
adult_utterances_age <- dplyr::filter(adult_utterances, target_child_age < 36)
adult_utterances_age_corpus <- dplyr::filter(adult_utterances_age, corpus_name %in% c("Clark", "Brown"))
```

```{r childes-2}
library(childesr)
all_utterances <- get_utterances(language = "eng")
all_utterances_age <- dplyr::filter(all_utterances, target_child_age < 36)
all_utterances_age_corpus <- dplyr::filter(all_utterances_age, corpus_name == "Clark", "Brown")
```

```{r childes-2}
library(childesr)
child_utterances <- get_utterances(role = c("Target_Child", "Child"), language = "eng")
child_utterances_age <- dplyr::filter(child_utterances, target_child_age < 36)
child_utterances_age_corpus <- dplyr::filter(adult_utterances_age, corpus_name %in% c("Clark", "Brown"))
```

```{r childes-2}
library(childesr)
d_adam_prod <- get_tokens(corpus = "Brown",
                          role = "target_child",
                          token = c("dog", "ball"))
```

```{r childes-2}
library(childesr)
get_contexts(target_child = "Shem", token = c("dog", "ball"))
```

```{r childes-2}
write.csv(adult_utterances, "adult_utterances.csv")
```

```{r childes-2}
write.csv(adult_utterances_age, "adult_utterances_age.csv")
```

```{r childes-2}
write.csv(adult_utterances_age_corpus, "adult_utterances_age_corpus.csv")
```

```{r childes-2}
write.csv(child_utterances_age, "child_utterances_age.csv")
```

```{r childes-2}
write.csv(child_utterances_age_corpus, "child_utterances_age_corpus.csv")
```

```{r childes-2}
write.csv(all_utterances_age, "all_utterances_3.csv")
```

```{r childes-2}
write.csv(all_utterances_age, "all_utterances_3.csv")
```

```{r childes-2}
library(dplyr)
df_0 <- `concept_and_instance_all_n=0` %>%
    mutate(age = cut(V6, c(0, 36))) %>% 
    mutate(wndw = 0) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_1 <- `concept_and_instance_all_n=1` %>%
    mutate(age = cut(V6, c(0,36))) %>% 
    mutate(wndw = 1) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_2 <- `concept_and_instance_all_n=2` %>%
    mutate(age = cut(V6, c(0,36))) %>% 
    mutate(wndw = 2) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_3 <- `concept_and_instance_all_n=3` %>%
    mutate(age = cut(V6, c(0, 36))) %>% 
    mutate(wndw = 3) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
dfMerge <- do.call("rbind", list(df_0, df_1, df_2, df_3))
```

```{r childes-2}
library(ggplot2)
p <- ggplot(dfMerge, aes(age, count, colour=V5)) + 
    geom_line() + 
    geom_point()
p + facet_grid(rows = vars(wndw))
p
```


```{r childes-2}
library(ggplot2)
p <- ggplot(dfMerge, aes(age, count, colour=V5)) + 
    geom_line(aes(group = V5)) + geom_point(aes(group = V5)) + 
    facet_grid(rows = vars(wndw), vars(V1))
p
```

Make weightings
```{r}
dfMerge <- mutate(dfMerge, weight = count * (1/(wndw + 1)))
```

Sum all weights across windows
```{r}
dfSum <- dfMerge %>% group_by(V1, V5) %>%
  summarize(weight = sum(weight))
```


Create similarity matrix for explicit cues using a vectorial representation:
```{r}
library(tidyr)
library(tidyverse)
df <- spread(dfSum, V1, weight, fill=0)
df <- df %>% remove_rownames %>% column_to_rownames(var="V5")
```

```{r}
write.csv(df, "vectors_n<=3.csv")
```

Check this function!!!! Calculate cosine similarity
```{r}
library(text2vec)
cos_sim <- sim2(as.matrix(df), as.matrix(df), method="cosine")
```

Is there a way to get this with categories organized?
```{r}
library(ggcorrplot)
library(ggplot2)

reorder_cormat <- function(cos_sim){
# Use correlation between variables as distance
dd <- as.dist((1-cos_sim)/2)
hc <- hclust(dd)
cos_sim <- cos_sim[hc$order, hc$order]
}

get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
}

cos_sim <- reorder_cormat(cos_sim)
lower_tri <- get_lower_tri(cos_sim)
heatmap <- ggcorrplot(lower_tri) + theme(axis.text.x = element_text(size=9), axis.text.y = element_text(size=9))
heatmap

png("heatmap.png", width = 1600, height = 1600)
plot(heatmap)
dev.off()
```


