---
title: "Concepts Analysis"
author: "Kyra Wilson"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

library(childesr) 
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(text2vec)
library(ggcorrplot)
library(factoextra)
library(cluster)
library(wordVectors)
library(reshape2)
library(pROC)
library(extraDistr)
library(NbClust)
library(knitr)
library(feather)

`%!in%` = Negate(`%in%`)
```

##Data gathering

We begin by getting utterances from childes-db. The default option is returning all non-child English utterances spoken to children 3 years of age or youger
```{r eval = FALSE, echo = FALSE}
get_childes_utterances <- function(){
  adult_utterances <- get_utterances(db_version="2018.1", role_exclude = c("Target_Child", "Child"), language = "eng")
  adult_utterances <- dplyr::filter(adult_utterances, target_child_age < 72)
  #write.csv(adult_utterances, "pydata/adult_utterances_6.csv")
  adult_utterances <- dplyr::filter(adult_utterances, target_child_age < 60)
  #write.csv(adult_utterances, "pydata/adult_utterances_5.csv")
  adult_utterances <- dplyr::filter(adult_utterances, target_child_age < 48)
  #write.csv(adult_utterances, "pydata/adult_utterances_4.csv")
  adult_utterances <- dplyr::filter(adult_utterances, target_child_age < 36)
  #write.csv(adult_utterances, "pydata/adult_utterances_3.csv")
  return(adult_utterances)
}

adult_utterances <- get_childes_utterances()
```

#Save files for individual age ranges
```{r eval = FALSE, echo = FALSE}
file <- "pydata/adult_utterances_6.csv"
utterances <- read_csv(file, show_col_types=FALSE)
a_utterances <- dplyr::filter(utterances, target_child_age > 36 & target_child_age <= 48)
write.csv(a_utterances, "pydata/adult_utterances_3-4.csv", row.names=FALSE)
b_utterances <- dplyr::filter(utterances, target_child_age > 48 & target_child_age <= 60)
write.csv(b_utterances, "pydata/adult_utterances_4-5.csv", row.names=FALSE)
c_utterances <- dplyr::filter(utterances, target_child_age > 60 & target_child_age <= 72)
write.csv(c_utterances, "pydata/adult_utterances_5-6.csv", row.names=FALSE)
```

<!-- Need to add back code to get things from wordbank -->
<!-- May need to reorganize top chunks of code -->

Retrieve number of individual children (and their ages) and transcripts used in analysis
```{r}
for (var in c("3", "4", "5", "6")){
  file <- paste("pydata/adult_utterances_", var, ".csv", sep='')
  utterances <- read_csv(file, show_col_types=FALSE)
  meta_child <- count(utterances, target_child_id)
  meta_transcript <- count(utterances, transcript_id)
  meta_ages <- unique(select(utterances, c('target_child_id', 'target_child_age')))
  print(paste('AGES <', var, 'YRS', sep=''))
  print(c('Number of utterances:', nrow(utterances)))
  print(c('Number of words:', sum(str_count(utterances$gloss, '\\s+')+1, na.rm=TRUE)))
  print(c('Number of children:' , nrow(meta_child)))
  print(c('Number of transcripts:' , nrow(meta_transcript)))
  print(c('Mean age:', mean(meta_ages$target_child_age)))
  print(c('Median age:', median(meta_ages$target_child_age)))
  print(c('SD age:', sd(meta_ages$target_child_age)))
}
```

Calculate proportion of explicit (interactive) categorization utterances relative to all utterances in a given category
```{r}
explicit_files = c("rdata/explicit_categorization_3.csv", "rdata/explicit_categorization_4.csv","rdata/explicit_categorization_5.csv", "rdata/explicit_categorization_6.csv")

totals3 = c("animal" = 3849, "toy" = 5515, "vehicle" = 157, "clothes" = 1942, "furniture"= 156, "food" = 2979)
totals4 = c("animal" = 4961, "toy" = 7093, "vehicle" = 167, "clothes" = 2497, "furniture"= 243, "food" = 4017)
totals5 = c("animal" = 5638, "toy" = 8334, "vehicle" = 187, "clothes" = 2777, "furniture"= 278, "food" = 4973)
totals6 = c("animal" = 6110, "toy" = 8637, "vehicle" = 191, "clothes" = 2861, "furniture"= 284, "food" = 5309)
totals <- list(totals3, totals4, totals5, totals6)

for (age in 1:length(explicit_files)){
    explicit_categorization <- read.csv(explicit_files[age], header = FALSE)
    explicit_proportion <- count(explicit_categorization, V1)
    explicit_proportion <- cbind(explicit_proportion, Proportion = explicit_proportion$n/totals[[age]][names(totals[[age]]) == explicit_proportion$V1])
    #print(paste("Ratio of Explicit Categorization to Category Occurrences for Age < ", toString(age + 2)))
    comment(explicit_proportion) <-paste("Ratio of Explicit Categorization to Category Occurrences for Age < ", toString(age + 2))
    print(explicit_proportion)
    kable(explicit_proportion, digits = 5, caption = paste("Ratio of Explicit Categorization to Category Occurrences for Age < ", toString(age + 2)))
}
```

##Explicit co-occurrences

To get co-occurrences of categories, run explicit_cues.py with files adult_utterances3.csv and wb_nouns_edited.csv.

##Helper functions

Given word vectors from w2v and list of words, return cosine similarity of all word pairs.
```{r include=FALSE}
get_w2v_cosSim <- function(filename, instances, age){
  model = train_word2vec(filename,
                         output="all_utterances_3_w2v.bin", threads = 4,
                         vectors = 100, window=10, cbow=1, min_count = 10, force= TRUE)
  
  model_cds = read.vectors("all_utterances_3_w2v.bin")
  model_cue_cds <- model_cds[[which(rownames(model_cds) %in% instances), average=FALSE]]
  w2v_filename <- paste("rdata/rds/", age, "_vectors_w2v.rds", sep="")
  #saveRDS(model_cue_cds, file = w2v_filename)
  cosSim_cds <- cosineSimilarity(model_cue_cds, model_cue_cds)
  return(cosSim_cds)
}
```

Given word vectors from explicit co-occurrence, return cosine similarity of all word pairs.
```{r include=FALSE}
#Could clean up this function

get_explicit_cosSim <- function(filename, age, cue_type){
  
    df_0 <- read.csv(filename, header = FALSE)  %>%
    mutate(wndw = 0) %>%
    group_by(wndw, V1, V5) %>%
    summarise(count=n())
  
  dfMerge <- do.call("rbind", list(df_0))
  dfMerge <- mutate(dfMerge, weight = count * (1/(wndw + 1)))
  dfSum <- dfMerge %>% group_by(V1, V5) %>%
    summarise(weight = sum(weight))
  df <- spread(dfSum, V1, weight, fill=0)
  df_filename <- paste("rdata/rds/", age, "_vectors_explicit.rds", sep="")
  #saveRDS(df, file = df_filename)
  df <- df %>% remove_rownames %>% column_to_rownames(var="V5")
  cos_sim <- sim2(as.matrix(df), as.matrix(df), method="cosine")
  return(cos_sim)
}
```

Given cosine similarity and a distance matrix, return the optimal number of clusters for the data based on median of 3 cluster measures (kl, gap, silhouette). 
```{r optimal_nbcluster}
#This could theoretically do everything for clustering, so maybe simplify code in the future

optimal_nbcluster <- function(sim_data, dis){
  vals <- c(0, 0, 0)
  
  vals[1] <- NbClust(data = sim_data, diss = dis, distance = NULL, min.nc = 1, max.nc = 10, method = "average", index = "kl")$Best.nc[1]
  
  vals[2] <- NbClust(data = sim_data, diss = dis, distance = NULL, min.nc = 1, max.nc = 10, method = "average", index = "gap")$Best.nc[1]
  
  vals[3] <- NbClust(data = sim_data, diss = dis, distance = NULL, min.nc = 1, max.nc = 10, method = "average", index = "silhouette")$Best.nc[1]
  
  optimal_clust_size <- median(vals)
  return(optimal_clust_size)
}
```

Given cosine similarities, return a clustering of the words. 
```{r include=FALSE}
get_clust <- function(cosSim){
  # Hierarchical clustering using Complete Linkage
  # Dissimilarity matrix
  d <- dist(cosSim, method = "euclidean")
  
  # Hierarchical clustering using Complete Linkage
  hc1 <- hclust(d, method = "average" )
  
  #Figure out whether to superimpose cluster size or find optimal
  #clust <- cutree(hc1, k = optimal_nbcluster(cosSim, d))
  clust <- cutree(hc1, k = 6)
  
  return(clust)
}
```

Given cosine similarities and mapping of instances and their categories, calculate the densities of similarities within an between clusters. 
```{r include=FALSE}

within_between_measure <- function(cosSim, cue_df){
  density_df <- data.frame()

  sim_long <- melt(cosSim) %>%
  cbind(cat1 = NA, cat2 = NA, age = 3, measure = NA)
  sim_long$Var1 <- as.character(sim_long$Var1)
  sim_long$Var2 <- as.character(sim_long$Var2)
  
  #Getting category names
  for (row in 1:nrow(sim_long)){
    
    word1 <- as.character(sim_long$Var1[row])
    word2 <- as.character(sim_long$Var2[row])
    
    sim_long$cat1[row] <- cue_df[word1, ]
    sim_long$cat2[row] <- cue_df[word2, ]
    
  }
  sim_long <- sim_long[!is.na(sim_long$cat1) & !is.na(sim_long$cat2), ]
  sim_long[sim_long$cat1 == sim_long$cat2, ]$measure <- "within"
  sim_long[sim_long$cat1 != sim_long$cat2, ]$measure <- "between"
  return(density_df <- rbind(density_df, sim_long))

}
```

Given a dataframe with within- and between-category densities, plot the densities
```{r include=FALSE}
density_plot <- function(density_df){
return(ggplot(density_df, aes(value, fill = measure)) + geom_density(alpha = 0.2) + facet_wrap(vars(age, cat1), scales="free_y"))
}
```

Given a ataframe with within- and between-category densities and list of instances, calculate the AUC for each category
```{r include=FALSE}
#clean this function up as well
auc_measure <- function(density_df, cue_words){

auc_df <- data.frame(matrix(ncol = length(cue_words), nrow = 0))
x <- names(cue_words)
colnames(auc_df) <- x

for (var in unique(density_df$cat1)){
  for (num in unique(density_df$age)){
    
    density_df2 <- density_df[density_df$cat1 == var & density_df$age == num, ]
    density_df2$measure[density_df2$measure == "between"] <- 0
    density_df2$measure[density_df2$measure == "within"] <- 1
    density_df2$measure <- as.numeric(density_df2$measure)
    
    auc_df[num - 2, var] <- auc(response = density_df2$measure, predictor = density_df2$value)
  }
}

return(auc_df)
}
```

Given cosine similarities and a list of instances, replicate Bornstein and Arterberry 2010 experiment.
```{r replicate_experiment, include=FALSE}
replicate_experiment <- function(cosSim, cue_words){
  
  all_list <- list()
  concept_combos <- combn(names(cue_words), 2)
  
  if(length(concept_combos)==2){
    comboLength <- 1
  }
  else if(length(concept_combos)>2){
    comboLength <- length(concept_combos[1, ])
  }
  
  for (combo in 1:comboLength){
    if (comboLength == 1){
      concept1 <- concept_combos[1]
      concept2 <- concept_combos[2]
    }
    else{
      concept1 <- concept_combos[1, combo]
      concept2 <- concept_combos[2, combo]
    }
    catRun <- list()
    run <- as.numeric()
    
    for (i in 1:250){
      count <- 0
      
      concept1words <- cue_words[[concept1]][which(cue_words[[concept1]] %in% row.names(cosSim))]
      concept2words <- cue_words[[concept2]][which(cue_words[[concept2]] %in% row.names(cosSim))]
      
      sample_group <- c(sample(concept1words, 4), sample(concept2words, 4))
      
      #make a categorical distribution w/ cosine similarities as probabilities
      count <- count + 1
      first <- sample(sample_group, replace = FALSE, 1)
      continue <- TRUE
      
      while(continue){
        sample_group <- sample_group[sample_group != first]
        
        #Probabilistically choose the next instance
        # temp_probability <- c()
        # for (instance in sample_group){
        #   temp_probability <- c(temp_probability, 1 + cosSim[first, instance])
        # }
        # probability <- temp_probability/sum(temp_probability)
        #next_instance <- sample_group[rcat(1, probability)]
        
        #Deterministically choose next instance
        temp_cosSim <- select(as.data.frame(cosSim), one_of(sample_group))[first, ]
        next_instance <- colnames(temp_cosSim)[which.max(temp_cosSim)]
        
        #check if category of first and next are the same
        if (first %in% cue_words[[concept1]] & next_instance %in% cue_words[[concept1]] | first %in% cue_words[[concept2]] & next_instance %in% cue_words[[concept2]]){
          count <- count + 1
          first <- next_instance
          if (count == 4){
            run <- c(run, count)
            count <- 0
            continue <- FALSE
          }
        }
        else{
          run <- c(run, count)
          count <- 0
          continue <- FALSE
        }
      }
    }
  all_list[[concept1]][[concept2]] <- run
  }
  return(all_list)
}

```

Given cosine similarities and a list of instances, replicate Bornstein and Arterberry 2010 experiment with random probabilities as a control.
```{r randomize_experiment, include=FALSE}
randomize_experiment <- function(cosSim, cue_words){
  all_list <- list()
  concept_combos <- combn(names(cue_words), 2)
  
  if(length(concept_combos)==2){
    comboLength <- 1
  }
  else if(length(concept_combos)>2){
    comboLength <- length(concept_combos[1, ])
  }
  
  for (combo in 1:comboLength){
    if (comboLength == 1){
      concept1 <- concept_combos[1]
      concept2 <- concept_combos[2]
    }
    else{
      concept1 <- concept_combos[1, combo]
      concept2 <- concept_combos[2, combo]
    }
    catRun <- list()
    run <- as.numeric()
    
    for (i in 1:250){
    count <- 0
    concept1words <- cue_words[[concept1]][which(cue_words[[concept1]] %in% row.names(cosSim))]

    concept2words <- cue_words[[concept2]][which(cue_words[[concept2]] %in% row.names(cosSim))]
    
    sample_group <- c(sample(concept1words, 4), sample(concept2words, 4))
    
    #make a categorical distribution w/ cosine similarities as probabilities
    count <- count + 1
    first <- sample(sample_group, replace = FALSE, 1)
    continue <- TRUE
    
    while(continue){
      sample_group <- sample_group[sample_group != first]
      
      #Randomly choose next instance
      probability <- rep(1/length(sample_group), length(sample_group))
      next_instance <- sample_group[rcat(1, probability)]
      
      #check if category of first and next are the same
      if (first %in% cue_words[[concept1]] & next_instance %in% cue_words[[concept1]] | first %in% cue_words[[concept2]] & next_instance %in% cue_words[[concept2]]){
        count <- count + 1
        first <- next_instance
        if (count == 4){
          run <- c(run, count)
          count <- 0
          continue <- FALSE
        }
      }
      else{
        run <- c(run, count)
        count <- 0
        continue <- FALSE
      }
    }
    }
  all_list[[concept1]][[concept2]] <- run
}
return(all_list)
}
```

Given AUC measures for w2v, random, and optional explicit cues, plot the results of the experiments. 
```{r experiment_plot, include=FALSE}
#Graph experiment results
experiment_plot <- function(w2v, random, explicit){
  experiment_df_w2v <- melt(w2v) %>%
    cbind(mode='w2v')
  experiment_df_random <- melt(random) %>%
    cbind(mode='random')
  
  if(missing(explicit)){
    experiment_df_w2v <- rbind(experiment_df_w2v, experiment_df_random) %>%
    mutate(pair=paste(L1, L2, sep=" & "))
  }
  else{
    experiment_df_explicit <- melt(explicit) %>%
    cbind(mode='explicit')
    experiment_df_w2v <- rbind(experiment_df_explicit, experiment_df_w2v, experiment_df_random) %>%
    mutate(pair=paste(L1, L2, sep=" & "))
  }
  return(ggplot(data=experiment_df_w2v, aes(x=stringr::str_wrap(pair, 10), y=value, fill=mode)) +
  geom_bar(stat="summary", fun.y="mean", position=position_dodge()) + 
  geom_errorbar(stat="summary", fun.data="mean_se", width=0.1, position = position_dodge(0.9)) + ggtitle("Experiment Replication") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue", "deeppink4")) + theme(axis.text.x = element_text(angle = 90)) + xlab("Pairs") + ylim(0, 4))
  
}
```

##Main functions

First, get list of categories and instances and reorganize them so they can be used in later functions.
```{r main, include=FALSE}
#Need to remove toy, animal, food, from unique items
unique_items <- readRDS("rdata/rds/unique_items.rds")
categories <- c("toys", "food_drink", "animals", "clothing", "furniture_rooms", "vehicles")
cue_words <- unique_items[categories]
cue_words_df <- melt(cue_words) %>%
      remove_rownames %>% column_to_rownames(var="value")
instances <- unlist(cue_words)
```

```{r}
txt_files <- c("rdata/adult_utterances_3-4.txt", "rdata/adult_utterances_4-5.txt","rdata/adult_utterances_5-6.txt")
age_str <- str_match(txt_files[0], "_([0-9,\\-]*).txt")[2]
print(age_str)
w2v_file <- paste("rdata/rds/", age_str, "_cosSim_w2v.rds", sep="")


```

Get cosine similarity (density plot), AUC, development up to 6, and 2-dimensional plot for w2v, explicit verb co-occurrence, and general co-occurrence
Also does developmental ranges (3-4, 4-5, 5-6)
```{r}
txt_files <- c("rdata/adult_utterances_3.txt", "rdata/adult_utterances_4.txt", "rdata/adult_utterances_5.txt", "rdata/adult_utterances_6.txt", "rdata/adult_utterances_3-4.txt", "rdata/adult_utterances_4-5.txt","rdata/adult_utterances_5-6.txt")
concept_files <- c("rdata/concepts_and_instances_all_3.csv", "rdata/concepts_and_instances_all_4.csv", "rdata/concepts_and_instances_all_5.csv", "rdata/concepts_and_instances_all_6.csv", "rdata/concepts_and_instances_all_3-4.csv", "rdata/concepts_and_instances_all_4-5.csv", "rdata/concepts_and_instances_all_5-6.csv")
cooccurrence_files <- c("rdata/broad_concepts_and_instances_3.csv", "rdata/broad_concepts_and_instances_4.csv", "rdata/broad_concepts_and_instances_5.csv", "rdata/broad_concepts_and_instances_6.csv", "rdata/broad_concepts_and_instances_3-4.csv", "rdata/broad_concepts_and_instances_4-5.csv", "rdata/broad_concepts_and_instances_5-6.csv")

cohesion <- data.frame()

for (age in 1:length(txt_files)){
  print(txt_files[age])
  age_str <- str_match(txt_files[age], "_([0-9,\\-]*).txt")[2]
  print(age_str)
  w2v_file <- paste("rdata/rds/", age_str, "_cosSim_w2v.rds", sep="")
  explicit_file <- paste("rdata/rds/", age_str, "_cosSim_explicit.rds", sep="")
  cooccurrence_file <- paste("rdata/rds/", age_str, "_cosSim_cooccurrence.rds", sep="")
  
  print(w2v_file)
  if (!file.exists(txt_files[age])){
    w2v_cosSim <- get_w2v_cosSim(txt_files[age], instances, age_str)
    saveRDS(w2v_cosSim, w2v_file)
  }
  else{
    w2v_cosSim <- readRDS(w2v_file)
  }
  
  if (!file.exists(concept_files[age])){
    explicit_cosSim <- get_explicit_cosSim(concept_files[age], age_str)
    saveRDS(explicit_cosSim, explicit_file)
  }
  else {
    explicit_cosSim <- readRDS(explicit_file)
  }
  
  if (!file.exists(cooccurrence_files[age])){
    cooccurrence_cosSim <- get_explicit_cosSim(cooccurrence_files[age], age_str)
    saveRDS(cooccurrence_cosSim, cooccurrence_file)
  }
  else {
    cooccurrence_cosSim <- readRDS(cooccurrence_file)
  }
  
  explicit_clust_measure <- within_between_measure(explicit_cosSim, cue_words_df)
  w2v_clust_measure <- within_between_measure(w2v_cosSim, cue_words_df)
  cooccurrence_clust_measure <- within_between_measure(cooccurrence_cosSim, cue_words_df)
  
  plot(density_plot(explicit_clust_measure) + ggtitle(paste("Density of Verb Categorization for Age ", age_str)))
  plot(density_plot(w2v_clust_measure) + ggtitle(paste("Density of w2v Categorization for Age ", age_str))) 
  plot(density_plot(cooccurrence_clust_measure) + ggtitle(paste("Density of All Co-Occurrence Categorization for Age ", age_str))) 
  
  w2v_clust <- get_clust(w2v_cosSim)
  w2v_clust_file <- paste("rdata/rds/", age_str, "_clust_w2v.rds", sep="")
  saveRDS(w2v_clust, w2v_clust_file)
  #w2v_clust <- readRDS(w2v_clust_file)

  explicit_clust <- get_clust(explicit_cosSim)
  explicit_clust_file <- paste("rdata/rds/", age_str, "_clust_explicit.rds", sep="")
  saveRDS(explicit_clust, explicit_clust_file)
  #explicit_clust <- readRDS(explicit_clust_file)

  cooccurrence_clust <- get_clust(cooccurrence_cosSim)
  cooccurrence_clust_file <- paste("rdata/rds/", age_str, "_clust_cooccurrence.rds", sep="")
  saveRDS(cooccurrence_clust, cooccurrence_clust_file)
  #cooccurrence_clust <- readRDS(cooccurrence_clust_file)

  fviz_cluster(list(data = w2v_cosSim, cluster = w2v_clust), labelsize = 8, main = paste("w2v Cluster for Age ", age_str)) 
  fviz_cluster(list(data = explicit_cosSim, cluster = explicit_clust), labelsize = 8, main = paste("Verb Cluster for Age ", age_str))
  fviz_cluster(list(data = cooccurrence_cosSim, cluster = cooccurrence_clust), labelsize = 8, main = paste("Co-Occurrence Cluster for Age ", age_str)) 
  
  explicit_cohesion <- auc_measure(explicit_clust_measure, cue_words) %>%
    cbind(mode='verbs') %>% 
    melt() %>% 
    cbind(yr=age_str)
  w2v_cohesion <- auc_measure(w2v_clust_measure, cue_words) %>%
    cbind(mode='w2v') %>% 
    melt() %>% 
    cbind(yr=age_str)
  cooccurrence_cohesion <- auc_measure(cooccurrence_clust_measure, cue_words) %>%
    cbind(mode='cooccurrence') %>% 
    melt() %>% 
    cbind(yr=age_str)
  cohesion <- rbind(cohesion, explicit_cohesion, w2v_cohesion, cooccurrence_cohesion)
  
  plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode)) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle(paste("AUC for Age ", age_str)) + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue", "darkred")))
}

plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode)) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC across development") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue", "darkred")) + facet_grid(cols=vars(yr))+ theme(axis.text.x = element_text(angle = 90))) 
```

Get the cosine similarities for both w2v and explicit cues. (Can be read from file or recalculated.)
```{r, eval=FALSE}
w2v_file <- c("rdata/adult_utterances_3.txt")
explicit_file <- c("rdata/concepts_and_instances_all_3.csv")

#Getting cosine similarity and clusters
#w2v_cosSim <- get_w2v_cosSim(w2v_file, instances)
#saveRDS(w2v_cosSim, "rdata/rds/w2v_cosSim.rds")

w2v_cosSim <- readRDS("rdata/rds/w2v_cosSim.rds")
w2v_clust <- readRDS("rdata/rds/w2v_clust.rds")

#explicit_cosSim <- get_explicit_cosSim(explicit_file)
#saveRDS(explicit_cosSim, "rdata/rds/explicit_cosSim.rds")

explicit_cosSim <- readRDS("rdata/rds/explicit_cosSim.rds")
explicit_clust <- readRDS("rdata/rds/explicit_clust.rds")
```

Get the within- and between- similarity densities for each category.
```{r, eval=FALSE}
explicit_clust_measure <- within_between_measure(explicit_cosSim, cue_words_df)
w2v_clust_measure <- within_between_measure(w2v_cosSim, cue_words_df)
  
plot(density_plot(explicit_clust_measure) + ggtitle("Explicit Cohesiveness"))
plot(density_plot(w2v_clust_measure) + ggtitle("w2v Cohesiveness"))  
```

Using within- and between- similarities, calculate AUC for each of the categories.
```{r, eval=FALSE}
explicit_cohesion <- auc_measure(explicit_clust_measure, cue_words) %>%
  cbind(mode='explicit') %>% 
  cbind(type= NA) %>% 
  melt()
w2v_cohesion <- auc_measure(w2v_clust_measure, cue_words) %>%
  cbind(mode='w2v', type = NA) %>% 
  melt()
cohesion <- rbind(explicit_cohesion, w2v_cohesion)

cohesion$type[cohesion$variable != "furniture_rooms" & cohesion$variable != "animals"] <- "functional"
cohesion$type[cohesion$variable == "furniture_rooms" | cohesion$variable == "animals"] <- "perceptual"

plot(ggplot(data=cohesion[cohesion$mode=='explicit', ], aes(x=variable, y=value)) +
  geom_bar(stat="identity", position=position_dodge(), fill="darkcyan") + ylim(0, 1) + ggtitle("AUC of Explicit"))

plot(ggplot(data=cohesion[cohesion$mode=='w2v', ], aes(x=variable, y=value)) +
  geom_bar(stat="identity", position=position_dodge(), fill="darkslateblue") + ylim(0, 1) + ggtitle("AUC of w2v"))

plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode)) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue")))

plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode, alpha=type=="perceptual")) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue")) + 
  scale_alpha_discrete(guide='none'))

plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode, alpha=type=="functional")) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue")) + 
  scale_alpha_discrete(guide='none'))

```

Calculate cosine similarity, within- and between- similarities, and AUC for explicit cues with only category co-occurrence and not verb co-occurrence.
```{r, eval=FALSE}
explicit_file <- c("rdata/concepts_and_instances_categoryOnly_3.csv")

category_explicit_cosSim <- get_explicit_cosSim(explicit_file)
saveRDS(category_explicit_cosSim, "rdata/rdsexplicit_categoryOnly_cosSim_3.rds")

category_explicit_clust_measure <- within_between_measure(category_explicit_cosSim, cue_words_df)

plot(density_plot(category_explicit_clust_measure) + ggtitle("Explicit Cohesiveness w/o Verbs"))

category_explicit_cohesion <- auc_measure(category_explicit_clust_measure, cue_words) %>%
  cbind(mode='explicit') %>% 
  cbind(type= NA) %>% 
  melt()

plot(ggplot(data=category_explicit_cohesion, aes(x=variable, y=value, fill=mode)) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC w/o Verbs") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue")))

```

Visualize explicit and w2v clusters from cosine similarities
```{r, eval=FALSE}
w2v_clust <- get_clust(w2v_cosSim)
saveRDS(w2v_clust, "rdata/rds/w2v_clust.rds")
#w2v_clust <- readRDS("rdata/rds/w2v_clust.rds")

explicit_clust <- get_clust(explicit_cosSim)
saveRDS(explicit_clust, "rdata/rds/explicit_clust.rds")
#explicit_clust <- readRDS("rdata/rds/explicit_clust.rds")

cooccurrence_clust <- get_clust(cooccurrence_cosSim)
saveRDS(cooccurrence_clust, "rdata/rds/cooccurrence_clust.rds")
#cooccurrence_clust <- readRDS("rdata/rds/cooccurrence_clust.rds")

fviz_cluster(list(data = w2v_cosSim, cluster = w2v_clust), labelsize = 8) 
fviz_cluster(list(data = explicit_cosSim, cluster = explicit_clust), labelsize = 8) 
fviz_cluster(list(data = cooccurrence_cosSim, cluster = cooccurrence_clust), labelsize = 8) 
```

Calculate cosine similarity, within- and between- similarities, and AUC for different ages of children (right now does 3-6).
```{r, eval=FALSE}
txt_files <- c("rdata/adult_utterances_3.txt", "rdata/adult_utterances_4.txt", "rdata/adult_utterances_5.txt", "rdata/adult_utterances_6.txt")
concept_files <- c("rdata/concepts_and_instances_all_3.csv", "rdata/concepts_and_instances_all_4.csv", "rdata/concepts_and_instances_all_5.csv", "rdata/concepts_and_instances_all_6.csv")
cooccurrence_files <- c("rdata/broad_concepts_and_instances_3.csv", "rdata/broad_concepts_and_instances_4.csv", "rdata/broad_concepts_and_instances_5.csv", "rdata/broad_concepts_and_instances_6.csv")

cohesion <- data.frame()

for (age in 1:length(txt_files)){
  w2v_cosSim <- get_w2v_cosSim(txt_files[age], instances)
  w2v_file <- paste("rdata/rds/", toString(age + 2), "_cosSim_w2v.rds", sep="")
  saveRDS(w2v_cosSim, w2v_file)
  #w2v_cosSim <- readRDS(w2v_file)
  
  explicit_cosSim <- get_explicit_cosSim(concept_files[age])
  explicit_file <- paste("rdata/rds/", toString(age + 2), "_cosSim_explicit.rds", sep="")
  saveRDS(explicit_cosSim, explicit_file)
  #explicit_cosSim <- readRDS(explicit_file)
  
  cooccurrence_cosSim <- get_explicit_cosSim(concept_files[age])
  cooccurrence_file <- paste("rdata/rds/", toString(age + 2), "_cosSim_cooccurrence.rds", sep="")
  saveRDS(cooccurrence_cosSim, cooccurrence_file)
  #cooccurrence_cosSim <- readRDS(cooccurrence_file)
  
  explicit_clust_measure <- within_between_measure(explicit_cosSim, cue_words_df)
  w2v_clust_measure <- within_between_measure(w2v_cosSim, cue_words_df)
  cooccurrence_clust_measure <- within_between_measure(cooccurrence_cosSim, cue_words_df)
  
  explicit_cohesion <- auc_measure(explicit_clust_measure, cue_words) %>%
    cbind(mode='verbs') %>% 
    melt() %>% 
    cbind(yr=age+2)
  w2v_cohesion <- auc_measure(w2v_clust_measure, cue_words) %>%
    cbind(mode='w2v') %>% 
    melt() %>% 
    cbind(yr=age+2)
  cooccurrence_cohesion <- auc_measure(cooccurrence_clust_measure, cue_words) %>%
    cbind(mode='cooccurrence') %>% 
    melt() %>% 
    cbind(yr=age+2)
  cohesion <- rbind(cohesion, explicit_cohesion, w2v_cohesion, cooccurrence_cohesion)
}

plot(ggplot(data=cohesion, aes(x=yr, y=value, col=variable)) + geom_line() + ylim(0, 1) + ggtitle("AUC across development") + facet_grid(cols=vars(mode)))
plot(ggplot(data=cohesion, aes(x=yr, y=value, col=variable)) + geom_point() + ylim(0, 1) + ggtitle("w2v AUC across development"))

plot(ggplot(data=cohesion, aes(x=variable, y=value, fill=mode)) +
  geom_bar(stat="identity", position=position_dodge()) + ylim(0, 1) + ggtitle("AUC across development") + scale_fill_manual("legend", values = c("darkcyan", "darkslateblue")) + facet_grid(cols=vars(yr))+ theme(axis.text.x = element_text(angle = 90))) 
```

Replicate experiment from Bornstein and Arteberry 2010 for explicit categories with verb and category co-occurrence and w2v co-occurrence.
```{r, eval=FALSE}  
w2v_experiment <- replicate_experiment(w2v_cosSim, cue_words)
explicit_experiment <- replicate_experiment(explicit_cosSim, cue_words)
random_experiment <- randomize_experiment(explicit_cosSim, cue_words)

plot(experiment_plot(w2v_experiment, random_experiment, explicit_experiment))
```

Construct "animals" and "artifacts" categories. Calculate cosine similarity, within- and between- similarities, and AUC for w2v categorization of these categories.
```{r, eval=FALSE}
broad_categories <- c("animal", "artifact")
broad_cue_words <- list(artifacts = c(cue_words$toys, cue_words$furniture_rooms, cue_words$vehicles, cue_words$clothing), animals = c(cue_words$animals))
broad_cue_words_df <- melt(broad_cue_words) %>%
      remove_rownames %>% column_to_rownames(var="value")
broad_instances <- unlist(broad_cue_words)

broad_w2v_cosSim <- get_w2v_cosSim("rdata/broad_adult_utterances_3.txt", broad_instances)
saveRDS(broad_w2v_cosSim, "rdata/rds/broad_w2v_cosSim_3.rds")
#broad_w2v_cosSim <- readRDS("rdata/rds/broad_w2v_cosSim_3.rds")
#broad_explicit_cosSim <- get_explicit_cosSim("rdata/rds/broad_concepts_and_instances_3.csv")

broad_w2v_clust_measure <- within_between_measure(broad_w2v_cosSim, broad_cue_words_df)
plot(density_plot(broad_w2v_clust_measure) + ggtitle("Broad w2v Cohesiveness"))  
broad_w2v_cohesion <- auc_measure(broad_w2v_clust_measure, broad_cue_words_df) %>%
    cbind(mode='w2v') %>% 
    melt()

plot(ggplot(data=broad_w2v_cohesion, aes(x=variable, y=value)) +
  geom_bar(stat="identity", position=position_dodge(), fill="darkslateblue") + ylim(0, 1) + ggtitle("Implicit AUC of Animal vs. Artifact"))

# plot(ggplot(data=melt(broad_w2v_cohesion), aes(x=variable, y=value, fill=variable)) +
#   geom_bar(stat="identity") + ylim(0, 1) + ggtitle("Broad w2v AUC"))

```

Replicate experiment from Bornstein and Arteberry 2010 for "animal" and "artifacts" categories.
```{r, eval=FALSE}

broad_w2v_experiment <- replicate_experiment(broad_w2v_cosSim, broad_cue_words)
broad_random_experiment <- randomize_experiment(broad_w2v_cosSim, broad_cue_words)

plot(experiment_plot(broad_w2v_experiment, broad_random_experiment) + theme(axis.text.x = element_text(angle = 0)))
```


<!-- think more about chicken/fish problem--right now you just removed chicken from animal, and fish from food -->
<!-- remove these from wb_nouns_edited file too!!!!!! -->
