---
title: "concepts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(childesr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(text2vec)
```

Get all utterances from childes where language is English and age of target child is less than 3.
```{r}
all_utterances <- get_utterances(language = "eng")
all_utterances_age <- dplyr::filter(all_utterances, target_child_age < 36)
```

//Python script to generate a list of co-occurrences of basic terms and superordinate categories.//

Group responses by age range and count occurrences of basic term within superordinate categories. Then join together all dataframes for particular window sizes. 
```{r}
df_0 <- `concept_and_instance_all_n=0` %>%
    mutate(age = cut(V6, c(0, 36))) %>% 
    mutate(wndw = 0) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_1 <- `concept_and_instance_all_n=1` %>%
    mutate(age = cut(V6, c(0,36))) %>% 
    mutate(wndw = 1) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_2 <- `concept_and_instance_all_n=2` %>%
    mutate(age = cut(V6, c(0,36))) %>% 
    mutate(wndw = 2) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
df_3 <- `concept_and_instance_all_n=3` %>%
    mutate(age = cut(V6, c(0, 36))) %>% 
    mutate(wndw = 3) %>%
    group_by(wndw, V1, V5, age) %>%
    summarise(count=n())
dfMerge <- do.call("rbind", list(df_0, df_1, df_2, df_3))
```

Plot the number of co-occurrences of basic terms and superordinate categories as age increases according to superordinate category and window size.
```{r}
occurrence_change <- ggplot(dfMerge, aes(age, count, colour=V5)) + 
    geom_line(aes(group = V5)) + geom_point(aes(group = V5)) + 
    facet_grid(rows = vars(wndw), vars(V1))
```

Calculate weightings of each superordinate category for each basic term (number of co-occurrences * 1/window size+1), then sum weightings across all window sizes for equivalent basic terms. 
```{r}
dfMerge <- mutate(dfMerge, weight = count * (1/(wndw + 1)))
dfSum <- dfMerge %>% group_by(V1, V5) %>%
  summarize(weight = sum(weight))
df <- spread(dfSum, V1, weight, fill=0)
df <- df %>% remove_rownames %>% column_to_rownames(var="V5")
```

Calculate word-word similarity using cosine similarity for all word pairs.
```{r}
cos_sim <- sim2(as.matrix(df), as.matrix(df), method="cosine")
```

